HTW Data Dictionary

### 2023-07-21 Analysis/data_dictionary.qmd
reorg and rerender

+-----------+-----------+--------------------+
| Fruit     | Price     | Advantages         |
+===========+===========+====================+
| Bananas   | $1.34     | - built-in wrapper |
|           |           | - bright color     |
+-----------+-----------+--------------------+
| Oranges   | $2.10     | - cures scurvy     |
|           |           | - tasty            |
+-----------+-----------+--------------------+

: Sample grid table.

@@

>>>>

@@

### Numeric variables

| Variable Name | Description |
| ------------- | ----------- |
| trial         | Trial number |
| nGoodTrial    | Number of good trials |
| gt.bandStage  | Band stage in game time |
| gt.stage      | Stage in game time |
| gt.train      | Training in game time |
| input         | Input from the participant |
| bandInt       | Band interval |
| highBound     | High boundary of the velocity band |
| runTotal      | Running total of trials |
| dist          | Distance between produced x-velocity and the closest edge of the current velocity band |
| sdist         | Standardized distance |
| vx            | X-velocity of the projectile |
| vxb           | X-velocity at the boundary |
| vxi           | Initial X-velocity |
| vy            | Y-velocity of the projectile |
| nTrain        | Number of training trials |
| nTestNf       | Number of no-feedback testing trials |
| nInt          | Number of interleaved trials |
| nTestF        | Number of feedback testing trials |
| nTotal        | Total number of trials |
| lastTrain     | Last training trial |
| lastTrial     | Last trial |
